Analyses

### 2021-05-06 src/analysis/Analysis.Rmd
add analyses

---
title: 'Analyses'
author: 
output: 
  github_document:
    toc: yes
editor_options: 
  chunk_output_type: console
---

```{r "setup", include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE,
                      fig.align = "center",
                      fig.path=('../../report/figures/'))
library(printr)
options(digits = 2)
library(rmarkdown)
library(here)
```

# Scripts
- [Required Packages &amp; Reproducibility](#required-packages-&amp;-reproducibility)
- [Analyses](#analyses)
  - [Balance Checks](#balance-checks)
  - [Gender Hypothesis](#gender-hypothesis)
  - [Migration Hypothesis](#migration-hypothesis)
  - [Intersection Hypothesis](#intersection-hypothesis)
  - [Intersection Hypothesis -- Pooled](#intersection-hypothesis--pooled)

# Required Packages &amp; Reproducibility
```{r "env", message=FALSE, warning=F}
rm(list=ls())
source(here("src/lib/functions.R"))
```

# Analyses
```{r "data for analyses"}
load(here("data/intermediate/cleaned_data.RData"))
source(here("src/analysis/data-for-analyses.R"))
```

@@

methodnames <- setNames(as.list(descr$name), descr$name)
table <- purrr::map(descr, .f= ".") 
#render_j2("src/analysis/table_descriptives.tex.j2", "report/figures/table_descriptives.tex", data=list(data=table, methods=methodnames))
```

## Balance Checks
```{r "balance-checks", eval = F}
source(here("src/analysis/balance-test.R"))
```

## Gender Hypothesis 
```{r "h1", fig.align="center", fig.height=8, fig.width=8, eval = F}
source(here("src/analysis/h1.R"))
```

## Migration Hypothesis
```{r "h2", fig.align="center", fig.height=8, fig.width=8, eval = F}
source(here("src/analysis/h2.R"))
```

## Intersection Hypothesis
```{r "h3", fig.align="center", fig.height=8, fig.width=8, eval = F}
source(here("src/analysis/h3.R"))
```

## Intersection Hypothesis -- Pooled
```{r "h3-pooled", fig.align="center", fig.height=8, fig.width=8, eval = F}
source(here("src/analysis/h3-pooled.R"))
```

>>>>

---
title: 'Analyses'
author: 
output: 
  github_document:
  always_allow_html: true
editor_options: 
  chunk_output_type: console
---

```{r "setup", include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE,
                      fig.align = "center",
                      fig.path=('../../report/figures/'))
library(rmarkdown)
```

# Scripts
- [Required Packages &amp; Reproducibility](#required-packages-&amp;-reproducibility)
- [Analyses](#analyses)
  - [Descriptive Results](#descriptive-results)
  - [Balance Checks](#balance-checks)
  - [Gender Hypothesis](#gender-hypothesis)
  - [Migration Hypothesis](#migration-hypothesis)
  - [Intersection Hypothesis](#intersection-hypothesis)
  - [Intersection Hypothesis -- Pooled](#intersection-hypothesis--pooled)

# Required Packages &amp; Reproducibility
```{r "env", message=FALSE, warning=F}
rm(list=ls())
source(here::here("src/lib/functions.R"))
```

# Analyses
```{r "scaling variables"}
load(here("data/intermediate/cleaned_data.RData"))
source(here("src/analysis/scales.R"))
#kable(scales, digits = 2) %>%
#  kable_styling(full_width = F, position = "center")
```

```{r "data for analyses"}
source(here("src/analysis/data-for-analyses.R"))
```

## Check Missing Values
I employ the following criteria:

- If 10% or less of the values on the dimension are missing, then we re-code the missing values to the overall mean.
- If 11% or more of the values on the dimension are missing, then we re-code the missing values to a constant (for instance 0) and include a dummy variable indicating whether the response on the covariate was missing or not.

```{r "check missings"}
descr <- d %>%
  summarise(`DV: Trait Evaluation` = round(sum(is.na(PT1))/n(),2),
            `DV: Favorability` = round(sum(is.na(PT2))/n(),2),
            `DV: Representation` = round(sum(is.na(PT3))/n(),2),
            `DV: Career Prospects` = round(sum(is.na(PT4))/n(),2),
            `Immigration (%)` = round(sum(is.na(PreT1))/n(),2),
            `Position: Immigration` = round(sum(is.na(PreT2))/n(),2),
            `Position: Defense` = round(sum(is.na(PreT3))/n(),2),
            `Position: Education` = round(sum(is.na(PreT4))/n(),2),
            `Attitude: Women in Politics` = round(sum(is.na(PreT5))/n(),2),
            `Ideology` = round(sum(is.na(PreT6))/n(),2),
            `Political Efficacy (1)` = round(sum(is.na(PreT7_1))/n(),2),
            `Political Efficacy (2)` = round(sum(is.na(PreT7_2))/n(),2),
            `Political Efficacy (3)` = round(sum(is.na(PreT7_3))/n(),2),
            `Political Efficacy (4)` = round(sum(is.na(PreT7_4))/n(),2),
            `Political Efficacy (5)` = round(sum(is.na(PreT7_5))/n(),2),
            `Political Efficacy (6)` = round(sum(is.na(PreT7_6))/n(),2),
            `Political Efficacy (7)` = round(sum(is.na(PreT7_7))/n(),2),
            `Position: COVID-19` = round(sum(is.na(PreT8))/n(),2),
            `Gender` = round(sum(is.na(F1))/n(),2),
            `Age` = round(sum(is.na(F2))/n(),2),
            `Region` = round(sum(is.na(F3))/n(),2),
            `Urbaness` = round(sum(is.na(F4))/n(),2),
            `Migration Background` = round(sum(is.na(F5))/n(),2),
            `Party Preference` = round(sum(is.na(F6))/n(),2),
            `Employment` = round(sum(is.na(F7))/n(),2),
            `Income` = round(sum(is.na(F8))/n(),2),
            `Education` = round(sum(is.na(F9))/n(),2)) %>%
  pivot_longer(cols = `DV: Trait Evaluation`:`Education`,
              names_to = "Variables", values_to = "% Missing Values") %>%
  filter(`% Missing Values` > 0)

#kable(descr) %>%
#  kable_styling(full_width = F, position = "center")
```

I recode the missing values of the variables `Urbaness`, `Party Preference`, `Employment`, and `Income` to the mean value of the respective variables -- median for `Party Precerence`.
For Income, I also include a dummy indicating whether the missing value was imputed.

```{r "add missings"}
means <- d %>%
  summarise(F4 = round(mean(F4, na.rm = T),0),
            F5 = round(mean(F5, na.rm = T), 0),
            F6 = max(names(table(F6))),
            F7 = round(mean(F7, na.rm = T),0),
            F8 = round(mean(F8, na.rm = T),0),
            F9 = round(mean(F9, na.rm = T),0))

d <- d %>%
  mutate(F4 = replace_na(F4, means$F4),
         F5 = replace_na(F5, means$F5),
         F6 = replace_na(F6, means$F6),
         F7 = replace_na(F7, means$F7),
         missing_F8 = if_else(is.na(F8), 1, 0),
         F8 = replace_na(F8, means$F8),
         F9 = replace_na(F9, means$F9))
rm(means, descr, scales)
```

@@

methodnames <- setNames(as.list(descr$name), descr$name)
table <- purrr::map(descr, .f= ".") 
#render_j2("src/analysis/table_descriptives.tex.j2", "report/figures/table_descriptives.tex", data=list(data=table, methods=methodnames)
rm(descr, methodnames, table, fn, table2)
```

## Descriptive Results
```{r "descriptive-results", echo=FALSE, fig.height=10, fig.width=6}
d %>%
  select(PT1, PT2, PT3, PT4, issue, name, compromise) %>%
  mutate(PT1 = PT1 * 2) %>%
  pivot_longer(cols = PT1:PT4,
               names_to = "dvs") %>%
  mutate(dvs = recode(dvs,
                      `PT1` = "DV: Trait Evaluation",
                      `PT2` = "DV: Favorability",
                      `PT3` = "DV: Representation",
                      `PT4` = "DV: Career Prospects"),
         compromise = if_else(compromise==1, "Compromise", "No Compromise"),
         compromise = factor(compromise,
                             level = c("No Compromise", "Compromise"))) %>%
  unite("treatment", c("issue", "name"), sep = ": ") %>%
  group_by(treatment, compromise, dvs) %>%
  summarise(means = round(mean(value, na.rm=T),1),
            stdev = sd(value, na.rm=T)) %>%
  mutate(lower = means - (1.56 * stdev),
         upper = means + (1.56 * stdev),
         type = if_else(means <= 5, "below", "above")) %>%
  ggplot(aes(x = treatment, 
             y =means, label = means, color=type,
             ymin = lower, ymax = upper)) +
  geom_point(stat='identity', size=6)  +
  scale_color_manual(values = c("above"=fig_cols[3],
                                "below"=fig_cols[2])) +
  geom_errorbar(width = 0) +
  geom_text(color="white", size=2) +
  facet_grid(dvs~compromise) +
  labs(y = "0 (negative) - 10 (positive)", 
       x = "", title = "Bend or Break") +
  theme_minimal() +
  theme(plot.title = element_text(hjust = 0.5),
        plot.subtitle = element_text(hjust = 0.5),
        legend.position="none",
        legend.title = element_blank(),
        axis.text=element_text(size=8)) +
  geom_hline(yintercept = 5, linetype = "dotted", color = "darkgrey") +
  coord_flip() 
```

## Balance Checks

The figure below shows that the data is unbalanced for the variables: `Income`, `Employment`, `Urbaness`, `Age`, `Position: COVID`, `Political Efficacy`, `Ideology`,
`Attitudes: Women in Politics`, `Position: Education`, `Position: Defense`, `Position: Immigration`.
As described in the Pre-Analysis Plan (p.10), I will add these covariates to the analyses as controls.
```{r "balance-checks"}
source(here("src/analysis/balance-test.R"))
df
```

## Gender Hypothesis 
```{r "h1", fig.align="center", fig.height=8, fig.width=8}
source(here("src/analysis/h1.R"))
h1
```

## Migration Hypothesis
```{r "h2", fig.align="center", fig.height=8, fig.width=8}
source(here("src/analysis/h2.R"))
h2
```

## Intersection Hypothesis
```{r "h3", fig.align="center", fig.height=8, fig.width=8}
source(here("src/analysis/h3.R"))
h3
```

## Intersection Hypothesis -- Pooled
```{r "h3-pooled", fig.align="center", fig.height=8, fig.width=8}
source(here("src/analysis/h3-pooled.R"))
h3p
```
